---
title: "Marketing Campaign Performance Dashboard"
author: "Bhamini Raghuram Pillai"
format:
  dashboard:
    theme: cosmo
    orientation: rows
execute:
  echo: false
---

```{r}
library(tidyverse)
library(plotly)

marketing_data <- data.frame(
  Channel = c("Facebook", "Instagram", "Google", "Email", "YouTube"),
  Revenue = c(45000, 52000, 61000, 28000, 47000),
  Conversions = c(1200, 1350, 1600, 700, 1100),
  Spend = c(15000, 18000, 22000, 9000, 14000)
)
```

# Overview

## Row

### Total Revenue

```{r}
cat("$", format(sum(marketing_data$Revenue), big.mark = ","))
```

### Total Conversions

```{r}
cat(format(sum(marketing_data$Conversions), big.mark = ","))
```

## Row

### Revenue by Channel

```{r}
plot_ly(
  marketing_data,
  x = ~Channel,
  y = ~Revenue,
  type = "bar"
) %>%
layout(
  title = "Revenue Generated by Marketing Channel",
  xaxis = list(title = "Marketing Channel"),
  yaxis = list(title = "Revenue")
)
```

### Marketing Spend by Channel

```{r}
plot_ly(
  marketing_data,
  x = ~Channel,
  y = ~Spend,
  type = "scatter",
  mode = "lines+markers"
) %>%
layout(
  title = "Marketing Spend Across Channels",
  xaxis = list(title = "Marketing Channel"),
  yaxis = list(title = "Marketing Spend")
)
```

## Row

### Key Business Insights

-   Google generated the highest revenue among all marketing channels.
-   Email marketing had the lowest marketing spend.
-   Instagram and Google campaigns showed strong performance.
-   Marketing dashboards help businesses compare campaign effectiveness quickly.
